Cultural Transmission Can Explain the Evolution of Cooperative Behavior

### 2020-07-10 ms/main.tex
Fix results

We would like to know when $\hat{p}^*_2$ is legitimate equilibrium, i.e. $0<\hat{p}^*_2<1$.  
To do that we find the derivative  of $f(\hat{p})$,
\begin{equation} \label{eq:derivative_of_phattag-phat2}
  f'(\hat{p}) = 3\beta_0 \hat{p}^2 + 2\beta_1\hat{p}^2 + \beta_3
 \end{equation}
We assume that $T_A>T_B$ and we look on $\beta_1$:
\begin{equation} \label{eq:beta1}
  \begin{split}
   \beta_1 & = [c(1-v) -b (1-\alpha v)] \cdot(T_A-T_B) \\
   &< [c(1-\alpha v) - b(1-\alpha v)]\cdot(T_A-T_B) \\
   &= (1-\alpha v)(c-b)(T_A-T_B)
  \end{split}
 \end{equation}
From eq.~\ref{eq:beta1} we get that $\beta_1<0$ since $c-b<0$ $1-\alpha v>0$ and we assumed that $T_A > T_B$.
In this case the cubic $f(\hat{p})$ goes to infinity when $\hat{p}$ goes to minus infinity ($-\infty$). 
Therefore, if $\hat{p}^*_2$ is positive then $f'(0)$ must be negative % are you sure? I think it must be positive, because i think that the two extremes of a cubic must go in opposite directions DC: Yest, but I've fixed in the line before, there was minus sign missing
\begin{equation} \label{eq:derivative_of_phattag-phat_p=0}
  f'(0) = \beta_3
 \end{equation}
$\hat{p}^*_2>0$ when $\beta_3<0$.
In addition, $\hat{p}^*_0=0$ is stable when $|f'(0)|<1$ therefore, when $-1<\beta_3<1$.
We can show that
\begin{equation} \label{eq:beta3-condition}
  \beta_3 = \alpha bvT_A - cv(1-T_B) + (T_A-T_B) > -cv(1-T_B) > -1
\end{equation}
Therefore, when $\hat{p}^*_2>0$ we have $-1<\beta_3<0$ and $\hat{p}^*_0=0$ is locally stable.

Now we would like to find when $\hat{p}^*_2<1$.
If $T_A>T_B$, as before, then the cubic $f(\hat{p})$ goes to negative infinity when $\hat{p}$ goes to infinity.
Hence, if $\hat{p}^*_2<1$ then $f'(1)$ must be negative % again, i think that the two extremes of a cubic must go in opposite directions
\begin{equation} \label{eq:derivative_of_phattag-phat_p=1}
  f'(0) = \beta_1 - \beta_3
\end{equation}
Therefore, $\hat{p}^*_2<1$ when $\beta_1-\beta_3<0$.
In addition, $\hat{p}_1=1$ is stable when $|f'(1)|<1$ therefore, when $-1<\beta_1-\beta_3<1$. 
We show that when $0<\hat{p}^*_2<1$ hence $\beta_3<0$ and $\beta_1-\beta_3<0$ we get that $-1<\beta_1-\beta_3$: % cut down sentence to several sentences, it is too complex like this
\begin{equation} \label{eq:beta1-beta3-condition}
 \beta_1 - \beta_3 > - \beta_3 > 0 > -1 ,
\end{equation}
which means that when $0<\hat{p}^*_2<1$ then $\hat{p}^*_1=1$ is locally stable.

\textbf{Result 2.3}: if $\hat{p}^*_2$ is a legitimate equilibrium, then it is locally unstable.

\textbf{Result 2.4}: if $T_A>T_B$, then $\hat{p}^*_2$ is a legitimate equilibrium when $\beta_1<\beta_3<0$.

\textbf{Result 2.5}: if $T_B>T_A$, then $\hat{p}^*_2$ is a legitimate equilibrium when $\beta_1>\beta_3>0$.

>>>>

We would like to know when $\hat{p}^*_2$ is legitimate equilibrium, i.e. $0<\hat{p}^*_2<1$.  
To do that we find the derivative  of $f(\hat{p})$,
\begin{equation} \label{eq:derivative_of_phattag-phat2}
  f'(\hat{p}) = 3\beta_0 \hat{p}^2 + 2\beta_1\hat{p}^2 + \beta_3
 \end{equation}
We assume that $T_A>T_B$ and we look on $\beta_1$:
\begin{equation} \label{eq:beta1}
  \begin{split}
   \beta_1 & = [c(1-v) -b (1-\alpha v)] \cdot(T_A-T_B) \\
   &< [c(1-\alpha v) - b(1-\alpha v)]\cdot(T_A-T_B) \\
   &= (1-\alpha v)(c-b)(T_A-T_B)
  \end{split}
 \end{equation}
From eq.~\ref{eq:beta1} we get that $\beta_1<0$ since $c-b<0$ $1-\alpha v>0$ and we assumed that $T_A > T_B$.
In this case the cubic $f(\hat{p})$ goes to infinity when $\hat{p}$ goes to minus infinity ($-\infty$). 
Therefore, if $\hat{p}^*_2$ is positive then $f'(0)$ must be negative % are you sure? I think it must be positive, because i think that the two extremes of a cubic must go in opposite directions DC: Yest, but I've fixed in the line before, there was minus sign missing
\begin{equation} \label{eq:derivative_of_phattag-phat_p=0}
  f'(0) = \beta_3
 \end{equation}
$\hat{p}^*_2>0$ when $\beta_3<0$.
In addition, $\hat{p}^*_0=0$ is stable when $f'(0) = \beta_3 <0$.
Therefore, when $\hat{p}^*_2>0$ the coefficient $\beta_3$ must be negative and $\hat{p}^*_0=0$ is locally stable.

Now we would like to find when $\hat{p}^*_2<1$.
If $T_A>T_B$, as before, then the cubic $f(\hat{p})$ goes to minus infinity ($-\infty$) when $\hat{p}$ goes to infinity.
Hence, if $\hat{p}^*_2<1$ then $f'(1)$ must be negative % again, i think that the two extremes of a cubic must go in opposite directions. DC: I've double checked and I'm pretty sure my results are correct 
\begin{equation} \label{eq:derivative_of_phattag-phat_p=1}
  f'(1) = \beta_1 - \beta_3
\end{equation}
Therefore, $\hat{p}^*_2<1$ when $\beta_1-\beta_3<0$.
In addition, $\hat{p}^*_1=1$ is stable when $f'(1) = \beta_1-\beta_3<0$. 
We saw that when $0<\hat{p}^*_2<1$ the following must apply $f'(0)=\beta_3<0$ and $f'(1)=\beta_1-\beta_3<0$.
Hence, when $0<\hat{p}^*_2<1$ then $\hat{p}^*_1=1$ is locally stable.

\textbf{Result 4.1}: if $\hat{p}^*_2$ is a legitimate equilibrium, then it is locally unstable.

\textbf{Result 4.2}: if $T_A>T_B$, then $\hat{p}^*_2$ is a legitimate equilibrium when $\beta_1<\beta_3<0$.

\textbf{Result 4.3}: if $T_B>T_A$, then $\hat{p}^*_2$ is a legitimate equilibrium when $\beta_1>\beta_3>0$.
